Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-07 proposal/proposal.tex
Proposal stuff
Added citation for Roy's paper
Added content to related work

\title{CSCI 598A - Project Proposal}
\author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee\\ \emph{Undergraduates, EECS Department, Colorado School of Mines}}
\date{March 17, 2014}
ga

@@

\subsection{Related Work}
Fun work

@@

\section{Summary}
A summary \cite{someone2013}

\begin{thebibliography}{99}
\bibitem{someone2013} Somebody
\bibitem{johnson2012} X. Johnson
\end{thebibliography}

>>>>

\title{Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal}
\author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee\\ \emph{Undergraduates, EECS Department, Colorado School of Mines}}
\date{March 17, 2014}

@@

\subsection{Related Work}
\cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using a magnetometer and wireless nodes based on the commercially available Arduino Fio microcontroller platform. This system, uses the ubiquitous IEEE 802.15.4 communications standard to communicate automobile detection data to a central base-station based on the small, commercially available Raspberry Pi Linux computer. The project described in this proposal will augment and extend this project while collaborating closely with Stillwell, to the point of a real world deployment at the Colorado School of Mines.

@@

\section{Summary}
A summary \cite{johnson2012}

\begin{thebibliography}{99}
\bibitem{stillwell2013} R. Stillwell, A. Wilson ``Magnetometer Parking Sensor'' \emph{EGGN 383 Final Project, Colorado School of Mines}. December 12, 2013
\bibitem{johnson2012} X. Johnson
\end{thebibliography}
